---
title: "Untitled"
author: "Zoe Portlas"
date: "September 12, 2018"
output: 
  beamer_presentation: 
    colortheme: orchid
    fonttheme: structurebold
    theme: Antibes
---


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- \color{orange} Bullet 1
- \color{green} Bullet 2
- \color{red} Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, echo = FALSE}
plot(pressure)
```

## Incremental Bullets
> - almost
> - like
> - animation

## Using bigskip

For ...

\bigskip     
\bigskip     

Emphasis

## Trial Figure In \LaTeX

 \begin{picture}(320,250)
 \put(65,20){\includegraphics[height=8cm]{celtic.jpg}}
 \put(00,50){\begin{minipage}[t]{1\linewidth}
 \end{minipage}}
 \end{picture}
 
## Trial Figure In \LaTeX (2)

 \begin{picture}(320,250)
 \put(85,75){\includegraphics[height=6cm]{celtic.jpg}}
 \put(00,60){\begin{minipage}[t]{1\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}
 
## Trial Figure In \LaTeX (3)

 \begin{picture}(320,250)
 \put(0,20){\includegraphics[height=8cm]{celtic.jpg}}
 \put(180,180){\begin{minipage}[t]{0.4\linewidth}
 {Choose a point on the unit circle. Connect it to the origin with a line of length one, and denote the angle between that line and the horizontal coordinate axis by $\theta$.}
 \end{minipage}}
 \end{picture}