---
title: "Homework 4"
author: "Zoe Portlas"
date: "September 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Suppose x = 1.1, a = 2.2, and b = 3.3. Assign each expression to the value of the variable z and print the value stored in z.

$$x^{a^{b}}$$
```{r}
x <- 1.1
a <- 2.2
b <- 3.3

y <- a^b
z <- x^y
print(z)
```

$$(x^{a})^{b}$$
```{r}
x <- 1.1
a <- 2.2
b <- 3.3

y <- x^a
z <- y^b
print(z)
```

$$3x^{3}+2x^{2}+1$$
```{r}
x <- 1.1

z <- 3*x^3 + 2*x^2 +1
print(z)
```

2. Using the `rep()` and `seq()` functions, create the following vectors:

    a. (1,2,3,4,5,6,7,8,7,6,5,4,3,2,1)
```{r}
a <- c(seq(from = 1, to = 8), seq(from = 7, to = 1))
print(a)
```

    b. (1,2,2,3,3,3,4,4,4,4,5,5,5,5,5)
```{r}
b1 <- 1:5
b <- rep(x =b1, times = b1)
print(b)
```

    c. (5,4,4,3,3,3,2,2,2,2,1,1,1,1,1)
```{r}
c1 <- seq(from =5, to = 1)
c <- rep(x =c1, times = b1)
print(c)
```

3. Create a vector of two random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R's inverse trigonometry functions (`asin()`, `acos()`, or `atan()`), convert these numbers into polar coordinates (If you don't know what polar coordinates are, read about them on the web or in your calculus textbook).

```{r}
r <- runif(2)
print(r)
x <- r[1]
print(x)
y <- r[2]
print(y)
r <- sqrt(x^2 + y^2)
theta <- atan(y/x)
print(r)
print(theta)
```

4. Suppose that `queue <- c("sheep", "fox", "owl", "ant")` and that `queue` represents the animals that are lined up to enter Noah's Ark, with the sheep at the front of the line. Using R expressions, update the queue successively as 
    a. the serpent arrives;
    b. the sheep enters the ark;
    c. the donkey arrives and talks his way to the front of the line;
    d. the serpent gets impatient and leaves;
    e. the owl gets bored and leaves;
    f. the aphid arrives and the ant invites him to cut in line.
    g. Finally, determine the position of the aphid in line.

```{r}
queue <- c("sheep", "fox", "owl", "ant")
# Serpent arrives
queue <- c(queue, "serpent")
# Sheep enters ark
queue <- queue[-1]
# Donkey talks his way to front
queue <- c("donkey", queue)
# Serpent leaves
queue <- queue[-5]
# Owl leaves
queue <- queue[-3]
# Ant invites Aphid to cut in line
queue <- queue[-3]
queue <- c(queue, "aphid")
queue <- c(queue, "ant")
# Position of Aphid in line
print(queue)
# aphid is number 3 in line
```

5. Use R to create a vector of all the integers from 1 to 100 that are not divisible by 2, 3, or 7.

```{r}
p <- 1:100
p[!(!p%%2) + (!p%%3) + (!p%%7)]
```

6. 

`find: \t+`

`replace: ,`

7.

`find: (\w+), (\w+), (.*)`

`replace: \2 \1 (\3)`

Note: This didn't actually add the parentheses around `\3` for me.

8. 

To place the file names on their own lines:

`find: mp3\s`

`replace: mp3\r`

To place the 4-digit code at the end of the title:

`find: (\w+{4}) (.+).mp3`

`replace:\2_\1.mp3`

9.

First rearrangement:

`find: (\w)(\w+),(\w+),.+,(.+)`

`replace: \1_\3,\4`

Second rearrangement:

`find: (\w)(\w+),(\w{4})(\w+),.+,(.+)`

`replace: \1_\3,\5`